Rapid Cycleway Prioritisation Tool

### 2020-06-12 code/index.Rmd
Add link to travel to school data

- cycling potential (default metric to rank schemes)
- total length of cycling infrastructure created
- cycling potential x infrastructure length

@@

- Currently the tool has been developed primarily to help authorities prioritise the best locations for new cycleways. While it provides some indication of what a cohesive network might look like, it doesn't seek to prioritise what is the best type of intervention for a given location.
- The ranking of cycleways may not represent a proxy for which schemes are likely to deliver the best value for money. As a consequence this tool doesn't remove the need to use the Department for Transport's Active Mode Appraisal Toolkit ([AMAT](https://www.gov.uk/government/publications/tag-social-and-distributional-impacts-worksheets)) to assess whether proposed schemes deliver value for money.
- The best locations for new cycleways may not always be on roads with spare lanes. For example, in some circumstances it may be preferable for new cycleways to be along quiet roads running parallel to major arterial routes.
- The results for the 'top ranked new cycleways' doesn't identify routes under 500m with multiple changes of road name and doesn't identify short routes (under 500m) linking up existing cycleways. To address this limitation, the tool includes results labelled 'spare lane(s)' and 'estimated width >10m' which plug these gaps. These layers are hidden by default but can be found by clicking the 'layer' button in the top left corner of the map.
- The road network data is from 2017 and so will be slightly out-of-date.
- The model estimates the cycling potential of roads based on the estimated number of trips to and from work and school. Currently it is not possible to estimate cycling potential accounting for all journey purposes including shopping and leisure trips, which would significantly increase the estimated cycling potential.
- The PCT uses data from the 2011 Census and 2011 Cycle to School Census to estimate cycling potential. Hence the estimated cycling potential may represent an underestimate if there has been significant construction active in the area since 2011.
- The tool currently only identifies priority on-road routes for new cycleways. There may also be desirable off-road locations for new cycleways including alongside old railway lines or across open areas.
- Currently the tool allows for new cycleways on trunk roads with speeds of 40mph or more. While in some limited cases this may be desirable (e.g. where trunk roads are causing significant air pollution), in many cases it may not be desirable to reallocate road space from trunk roads to new cycleways. To address this, we have identify which top ranked routes have speed limits of 40mph or more in the tables.

>>>>

- cycling potential (default metric to rank schemes)
- total length of cycling infrastructure created
- cycling potential multiplied by road section length

@@

- Currently the tool has been developed primarily to help authorities prioritise the best locations for new cycleways. While it provides some indication of what a cohesive network might look like, it doesn't seek to prioritise what is the best type of intervention for a given location.
- The ranking of cycleways may not represent a proxy for which schemes are likely to deliver the best value for money. As a consequence this tool doesn't remove the need to use the Department for Transport's Active Mode Appraisal Toolkit ([AMAT](https://www.gov.uk/government/publications/tag-social-and-distributional-impacts-worksheets)) to assess whether proposed schemes deliver value for money.
- The best locations for new cycleways may not always be on roads with spare lanes. For example, in some circumstances it may be preferable for new cycleways to be along quiet roads running parallel to major arterial routes.
- The results for the 'top ranked new cycleways' doesn't identify routes under 500m with multiple changes of road name and doesn't identify short routes (under 500m) linking up existing cycleways. To address this limitation, the tool includes results labelled 'spare lane(s)' and 'estimated width >10m' which plug these gaps. These layers are hidden by default but can be found by clicking the 'layer' button in the top left corner of the map.
- The road network data is from 2017 and so will be slightly out-of-date.
- The model estimates the cycling potential of roads based on the estimated number of trips to and from work and school. Currently it is not possible to estimate cycling potential accounting for all journey purposes including shopping and leisure trips, which would significantly increase the estimated cycling potential.
- The PCT uses data from the 2011 Census and 2011 [National School Census](https://www.sciencedirect.com/science/article/pii/S2214140518301257) to estimate cycling potential. Hence the estimated cycling potential may represent an underestimate if new developments have been completed in the area since 2011.
- The tool currently only identifies priority on-road routes for new cycleways. There may also be desirable off-road locations for new cycleways including alongside old railway lines or across open areas.
- Currently the tool allows for new cycleways on trunk roads with speeds of 40mph or more. While in some limited cases this may be desirable (e.g. where trunk roads are causing significant air pollution), in many cases it may not be desirable to reallocate road space from trunk roads to new cycleways. To address this, we have identify which top ranked routes have speed limits of 40mph or more in the tables.
